### 2015-02-28 icfp15-servo/abstract.tex
Tighten the abstract a little, per kmc

In this paper, we show how a language with an affine type system and many syntactic
features familiar to functional language programmers can be successfully used to build
state-of-the-art systems software.
We also outline several pitfalls encountered along the way and describe some potential
areas for future research.
\end{abstract}

>>>>

In this paper, we show how a language with an affine type system, regions, and many syntactic
features familiar to functional language programmers can be successfully used to build
state-of-the-art systems software.
We also outline several pitfalls encountered along the way and describe some potential
areas for future research.
\end{abstract}
